\ifdefined\MAINTEXT \else Supplemental Material: \\ \fi Low-cost linear-scaling \emph{ab initio} molecular dynamics for weakly-interacting systems

### 2018-03-06 almo-langevin.tex
Changed figures
Used best data to update figures.
Edited Diff. Constant to match.

To test the accuracy of ALMO AIMD we used the trajectory analyzer TRAVIS~\cite{a:travis-main} to compute the infrared (IR) spectrum, RDF, and diffusion coefficient of liquid water from both the ALMO trajectory ($\epsilon_{\text{SCF}} = 10^{-2}$~a.u. and $R_{c} = 1.6$ vdWR) and from the reference trajectory. 
The diffusion coefficients $D_{\text{OT}}=\SI{1.9\pm0.9E-10}{\m^{2}\cdot\s^{-1}}$ and $D_{\text{ALMO}}=\SI{1.8\pm0.4E-10}{\m^{2}\cdot\s^{-1}}$ and RDFs (Figure~\ref{fig:dynproperties}a) are in good agreement. The quality of the ALMO IR spectrum (Figure~\ref{fig:dynproperties}c) is good despite minor errors in the intensity of the OH stretching mode, which is sensitive to the precise positions of the centers of localized orbitals. These stringent tests show that despite noticeable errors in the ALMO forces (Figure \ref{fig:randomforce}a), the compensating $R^{\Delta}(t)$ term in the modified Langevin equation makes it possible to recover atomic dynamics properly. We would like to note that ALMO AIMD could not be stabilized with $\Delta=0$. Neither were we able to find any values of $\Delta$ that stabilize trajectories generated using perturbative versions of ALMO DFT~\cite{a:almo-ls}.

@@

\begin{figure}[!htb]
\includegraphics[trim={0cm 0cm 0.1cm 0.1cm},clip,width=8.6cm]{Diffusion_Comparison.eps}
\caption{\label{fig:diffusion} Calculated mean-squared displacement function of water using ALMO DFT with $\epsilon_{\text{SCF}} = 10^{-2}$~a.u. and $R_{c} = 1.6$ vdWR.
Compared with equivalent MD run using OT DFT as a reference.
Calculations were performed at 298 K with the dispersion-corrected PBE $\mathrm{E_{XC}}$ functional and TZV2P basis set, using 125 water molecules for 10 ps.}
\end{figure}

>>>>

To test the accuracy of ALMO AIMD we used the trajectory analyzer TRAVIS~\cite{a:travis-main} to compute the infrared (IR) spectrum, RDF, and diffusion coefficient of liquid water from both the ALMO trajectory ($\epsilon_{\text{SCF}} = 10^{-2}$~a.u. and $R_{c} = 1.6$ vdWR) and from the reference trajectory. 
The diffusion coefficients $D_{\text{OT}}=\SI{1.7\pm0.1E-10}{\m^{2}\cdot\s^{-1}}$ and $D_{\text{ALMO}}=\SI{1.8\pm0.4E-10}{\m^{2}\cdot\s^{-1}}$ and RDFs (Figure~\ref{fig:dynproperties}a) are in good agreement. The quality of the ALMO IR spectrum (Figure~\ref{fig:dynproperties}c) is good despite minor errors in the intensity of the OH stretching mode, which is sensitive to the precise positions of the centers of localized orbitals. These stringent tests show that despite noticeable errors in the ALMO forces (Figure \ref{fig:randomforce}a), the compensating $R^{\Delta}(t)$ term in the modified Langevin equation makes it possible to recover atomic dynamics properly. We would like to note that ALMO AIMD could not be stabilized with $\Delta=0$. Neither were we able to find any values of $\Delta$ that stabilize trajectories generated using perturbative versions of ALMO DFT~\cite{a:almo-ls}.

@@

\begin{figure}[!htb]
\includegraphics[trim={2.4cm 0cm 3.0cm 1cm},clip,width=8.6cm]{Diffusion_Comparison.eps}
\caption{\label{fig:diffusion} Calculated mean-squared displacement function of water using ALMO DFT with $\epsilon_{\text{SCF}} = 10^{-2}$~a.u. and $R_{c} = 1.6$ vdWR.
Compared with equivalent MD run using OT DFT as a reference.
Calculations were performed at 298 K with the dispersion-corrected PBE $\mathrm{E_{XC}}$ functional and TZV2P basis set, using 125 water molecules for 10 ps.}
\end{figure}
